Shaping the Perception of a Robot as a Human-Like Agent by Cognitive Priming

### 2015-11-03 main.tex
Rewritten abstract

\abstract{
What leads us to attribute human-like characteristics to robots? The physical
appearance of the robot and the design of its behaviours do obviously play a key
role. This paper however reveals another mechanism at play, which is more subtle
and partially unconscious: the context of the interaction, and more precisely,
the cognitive prerequisites that the interaction presupposes.

To study this effect, we propose an original methodology based on eye-tracking
and a set of stimuli that are visually identical and yet induce different
assumptions regarding the cognitive capabilities of the robot. We then correlate
the gaze patterns with established questionnaires that assess anthropomorphic
attributions.

\begin{inparaenum}[\itshape a\upshape)]
As a result, we show that \item specific gaze patterns (fixations on the head of
the robot) correlate with post-hoc anthropomorphic
attributions, and hence, eye-tracking can be used as a novel \emph{in-the-moment}
metric of anthropomorphism, and \item simple context priming is sufficient
to elicit significantly different anthropomorphic attributions.
\end{inparaenum}

>>>>

\abstract{
What leads us to perceive robots as human-like agents? The physical appearance
of the robot and the design of its behaviours (the anthropomorphic \emph{design}
of the robot) do certainly play an important role. This paper sheds light on
another mechanism at play, less obvious because partially unconscious: the
cognitive skills that the interaction situation presupposes.

We evidence this effect with a novel methodology based on eye-tracking
and a set of stimuli that are visually identical and yet induce different
assumptions regarding the cognitive capabilities of the robot. By correlating
the resulting gaze patterns with answers to established questionnaires on
anthropomorphic attributions, we show that fixations on the head of the robot
indeed reflect how we perceive the machine.

Interestingly, we also show that humans appear quite sensitive to this effect:
even subtle context priming is sufficient to elicit significantly different
anthropomorphic attributions, and as such, this article provides new insights on
how our expectations of the robot's cognitive competency shape the bonds that we
build with the machine.
